---
title: "NFT Decentraland Trends Predictions and Analysis"
authors: "Nandita Gurwara, Shweta Mishra, Shailesh Chikne, Rishabh Chhaparia"
date: "04/01/2022"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
options(warn = -1)
library(rlang)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(modelr)
library(stringr)
library(ggpubr)
install.packages("htmlwidgets")
```


```{r warning=FALSE}
# Read the data from CSV files

nftdf <- read_csv("./NFT_Decentraland.csv", col_types = cols())

#Adding columns createdAt, updatedAt and expiresAt to the dataset
nftdf <- nftdf %>%
  mutate(
    createdAt = as.POSIXct(createdAt, origin = "1970-01-01"),
    updatedAt = as.POSIXct(updatedAt, origin = "1970-01-01"),
    expiresAt = as.POSIXct(expiresAt * 0.001, origin = "1970-01-01"),
    price = price / (10**18)
  )


df_split <- split(nftdf, nftdf$nftAddress)

for (i in 1:length(df_split)) {
  df_split[[i]] <- df_split[[i]] %>%
    mutate(sale_type = ifelse(createdAt == min(df_split[[i]]$createdAt),
      "Primary", "Secondary"
    ))
}

nftdf_updated <- bind_rows(df_split) %>%
  arrange(desc(createdAt))

nftdf_updated

```


```{r}
# Install package to read image
#install.packages("imager")
#library(stringr)
regexp <- "'image': '[^']*"
nftdf_updated$image <- str_match_all(nftdf_updated$nft, regexp) %>%
  str_replace_all("'image': '", "")

write.csv(nftdf_updated, "./NFT_Decentraland_Transformed.csv")

# method to load images
# load.image(nftdf_updated$image[1])
```

```{r echo=FALSE}
install.packages("psych")
library(psych)
nftdf_updated_tmp <- nftdf_updated %>%
mutate(category = case_when(category == "parcel" ~ 1,
category == "estate" ~ 2,
category == "ens" ~ 3,
category == "wearable" ~ 4 ))



ggplot(data = nftdf_updated_tmp, mapping = aes(x = category,
y = sale_type,
fill = log2(price))) +
geom_tile() +
labs(x = "Category", y = "Sale type", fill = "Price", title = 'Heatmap category v/s price')


corPlot(nftdf_updated_tmp[c('category', 'price')], cex = 1.2)
```

```{r}
#Top 5 NFTs per category as tables with images

#Install all the packages before running the code

library(gridExtra)
library(grid)
library(htmlwidgets)
library(webshot)
library(reactablefmtr)
library(tidyverse)
library(nflfastR)

#top5 with id 

top5 <- nftdf_updated %>% 
  select(category, price,image) %>%
  group_by(category) %>%
  arrange(desc(price)) %>%
  top_n(5,price)

#top 5 without id

top5_id <- nftdf_updated %>% 
  select(id,category, price,image) %>%
  group_by(category) %>%
  arrange(desc(price)) %>%
  top_n(5,price)

#filtering dataset by category

data_estate <- filter(top5,category=='estate')
data_parcel <- filter(top5,category=='parcel')
data_ens <- filter(top5,category=='ens')
data_wearable <-filter(top5,category=='wearable')

#install.packages("reactablefmtr")
#install.packages("nflfastR")
#install.packages("webshot")
#install.packages("htmlwidgets")
#webshot::install_phantomjs()


#Displaying top 5 estate as a table with respective images

reactable(data_estate)

reactable(data_estate,
          columns = list(image = colDef(cell = embed_img())))

df1 <- reactable(data_estate,
          columns = list(image = colDef(cell = embed_img(
            height = "50", width = "50"
          ))))

html_file1 <- "table1.html"
img_file1 <- "Estate.png"

#table1 <- reactable(df1)
saveWidget(widget = df1, file = html_file1, selfcontained = TRUE)
webshot(url = html_file, file = img_file1, delay = 0.1, vwidth = 500,vheight = 500)

```
```{r}

#Displaying top 5 wearable as a table with respective images

reactable(data_wearable)

reactable(data_wearable,
          columns = list(image = colDef(cell = embed_img())))

df2 <- reactable(data_wearable,
          columns = list(image = colDef(cell = embed_img(
            height = "50", width = "50"
          ))))

html_file2 <- "table2.html"
img_file2 <- "wearable.png"

#table <- reactable(df)
saveWidget(widget = df2, file = html_file2, selfcontained = TRUE)
webshot(url = html_file2, file = img_file2, delay = 0.1, vwidth = 500,vheight = 500)
```
```{r}
#Displaying top 5 parcel as a table with respective images

reactable(data_parcel)

reactable(data_parcel,
          columns = list(image = colDef(cell = embed_img())))

df3 <- reactable(data_parcel,
          columns = list(image = colDef(cell = embed_img(
            height = "50", width = "50"
          ))))

html_file3 <- "table2.html"
img_file3 <- "parcel.png"

#table <- reactable(df)
saveWidget(widget = df3, file = html_file3, selfcontained = TRUE)
webshot(url = html_file3, file = img_file3, delay = 0.1, vwidth = 500,vheight = 500)
```


```{r}
#setting theme for tables
#tt3 <- ttheme_minimal(
#  core=list(bg_params = list(fill = blues9[1:4], col=NA),
#            fg_params=list(fontface=3)),
#  colhead=list(fg_params=list(col="navyblue", fontface=4L)),
#  rowhead=list(fg_params=list(col="blue", fontface=3L)))

#png("Estate.png",height=300,width=1000)
#grid.table(as.data.frame(data_estate_new), theme =tt3)
#dev.off()
```

```{r}
#png("Parcel.png",height=300,width=1000)
#grid.table(as.data.frame(data_parcel), theme =tt3)
#dev.off()
```


```{r}
#Displaying ens as table

png("Ens.png",height=300,width=1000)
grid.table(as.data.frame(data_ens), theme =tt3)
dev.off()
```

```{r}
#png("Wearable.png",height=300,width=1500)
#grid.table(as.data.frame(data_wearable), theme =tt3)
#dev.off()
```

## Shweta - Some more visualizations

## A

## NFT distribution among categories

```{r echo=FALSE}
library(ggplot2)
ggplot(nftDf,aes(x=category))+
  geom_histogram(stat="count",aes(fill=category),show.legend = FALSE)+
labs(title="Wearable has the highest amount of NFTs",
     x="Different Categories of NFT")+
theme_classic()
```

## B

# Price and SD across ctaegories

```{r echo=FALSE}
library(ggplot2)
ggplot(nftDf,aes(x=category))+
  geom_boxplot(aes(y=log10(price),
                     fill=category),
                 show.legend = FALSE)+
labs(title="Estate has the highest average price
but the spread is more in Wearable.",
     x="Categories of NFT",
     y="Price of NFTs")+
theme_classic()
```

## C

# PRICE TRENDS OF TOP 5 

# adding createdAt column for Visualization

```{r tello}
top5_id1 <- nftDf %>% 
  select(id,category, price,image,createdAt) %>%
  group_by(category) %>%
  arrange(desc(price)) %>%
  top_n(5,price)
```

#trying to visualize each category in different plots, hence segregating the data, also adding createdAt column

```{r test}
data_estate1 <- filter(top5_id1,category=='estate')
data_parcel1 <- filter(top5_id1,category=='parcel')
data_ens1 <- filter(top5_id1,category=='ens')
data_wearable1 <- filter(top5_id1,category=='wearable')
```

```{r echo=FALSE}
library(ggplot2)
fun_color_range <- colorRampPalette(c("yellow", "black","red")) 
my_colors <- fun_color_range(20)
ggplot(top5_id1,aes(x=createdAt))+
  geom_point(aes(y=price
             ,color=price),alpha=0.1,size=0.07)+
scale_colour_gradientn(colors = my_colors)+   
labs(title="Change of NFT Price (in Crypto) over the years",
     x="Years",
     y="Price (in Crypto Currency)")+
facet_grid(~category)+ 
geom_smooth(aes(x=createdAt,
                y=price),
            color="Red",
            size=0.5)+
theme(axis.text.x=element_text(angle = 90))
```

# ESTATE : top 5 price trend 

```{r echo=FALSE}
library(ggplot2)
fun_color_range <- colorRampPalette(c("yellow", "black","red")) 
my_colors <- fun_color_range(20)
ggplot(data_estate1,aes(x=createdAt))+
  geom_point(aes(y=price
             ,color=price),alpha=0.1,size=0.07)+
scale_colour_gradientn(colors = my_colors)+   
labs(title="Change of NFT Price (in Crypto) over the years",
     x="Years",
     y="Price (in Crypto Currency)")+
geom_smooth(aes(x=createdAt,
                y=price),
            color="Red",
            size=0.5)+
theme(axis.text.x=element_text(angle = 90))
```

# PARCEL : top 5 price trend 

```{r echo=FALSE}
library(ggplot2)
fun_color_range <- colorRampPalette(c("yellow", "black","red")) 
my_colors <- fun_color_range(20)
ggplot(data_parcel1,aes(x=createdAt))+
  geom_point(aes(y=price
             ,color=price),alpha=0.1,size=0.07)+
scale_colour_gradientn(colors = my_colors)+   
labs(title="Change of NFT Price (in Crypto) over the years",
     x="Years",
     y="Price (in Crypto Currency)")+
geom_smooth(aes(x=createdAt,
                y=price),
            color="Red",
            size=0.5)+
theme(axis.text.x=element_text(angle = 90))
```

# ENS : top 5 price trend 

```{r echo=FALSE}
library(ggplot2)
fun_color_range <- colorRampPalette(c("yellow", "black","red")) 
my_colors <- fun_color_range(20)
ggplot(data_ens1,aes(x=createdAt))+
  geom_point(aes(y=price
             ,color=price),alpha=0.1,size=0.07)+
scale_colour_gradientn(colors = my_colors)+   
labs(title="Change of NFT Price (in Crypto) over the years",
     x="Years",
     y="Price (in Crypto Currency)")+
geom_smooth(aes(x=createdAt,
                y=price),
            color="Red",
            size=0.5)+
theme(axis.text.x=element_text(angle = 90))
```

# WEARABLE : top 5 price trend 

```{r echo=FALSE}
library(ggplot2)
fun_color_range <- colorRampPalette(c("yellow", "black","red")) 
my_colors <- fun_color_range(20)
ggplot(data_wearable1,aes(x=createdAt))+
  geom_point(aes(y=price
             ,color=price),alpha=0.1,size=0.07)+
scale_colour_gradientn(colors = my_colors)+   
labs(title="Change of NFT Price (in Crypto) over the years",
     x="Years",
     y="Price (in Crypto Currency)")+
geom_smooth(aes(x=createdAt,
                y=price),
            color="Red",
            size=0.5)+
theme(axis.text.x=element_text(angle = 90))
```


### Add wearable category
```{r}

nftDf <- read_csv("./NFT_Decentraland_Transformed.csv", col_types = cols())
regexp <- "'searchWearableCategory': '[^']*"
nftDf$wearableCategory <- str_match_all(nftdf_updated$nft, regexp) %>%
  str_replace_all("'searchWearableCategory': '", "")
nftDf$wearableCategory[nftDf$wearableCategory == "character(0)"] = NA
write.csv(nftDf, "./NFT_Decentraland_Transformed.csv")

```